### 2023-11-12 manuscript/manuscript.Rmd
fix sentence structure

Here, we outline the development of a data-driven, automated approach for 'first pass' putative molecular formula assignment in non-targeted, direct infusion and LC, ESI-MS based metabolomics data. 
This is aimed at biological experiments that include experimental classes with greater than four replicate samples and for the assignment of accurate masses up to 1000 atomic mass units (amu).
It is an ensemble approach that combines a number of annotation strategies including correlation analysis, molecular formula selection, adduct and isotopic scoring and graphical component selection.
This is accompanied by the development of the R package *assignments* as an implementation of the approach.

>>>>

Here, we outline the development of a data-driven, automated approach for 'first pass' putative molecular formula assignment in non-targeted ESI-MS based metabolomics data. 
This is aimed at biological experiments that include experimental classes with greater than four replicate samples and for the assignment of accurate masses up to 1000 atomic mass units (amu).
It is an ensemble approach that combines a number of annotation strategies including correlation analysis, molecular formula selection, adduct and isotopic scoring and graphical component selection.
This is accompanied by the development of the R package *assignments* as an implementation of the approach.
